A pipeline to analyse time-course gene expression data

### 2020-07-30 scripts/manuscript.Rmd
update to new moanin update on plot Centroid

These centroids are on a 0-1 scale, because of our rescaling of the spline
fits, and do not represent the actual gene expression level. In Figure \ref{fig:genesVsCentroids}, we plot a few
of the actual genes assigned to cluster 2 to see the difference:

```{r genesVsCentroids, fig.height=6, fig.width=6, fig.cap="Genes from cluster 2"}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
dataToPlot = rbind(
    assay(de_moanin_model[cluster2Genes[3:6],]), 
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
plot_splines_data(de_moanin_model, data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE, simpleY=FALSE,
    mar=c(1.5,2.5,2,0.1))
```

The spline plots are fitted per gene in the above plot and illustrate that
the genes assigned to a cluster have differing degrees to which their data
fits that of the cluster centroid, and indeed fits that of their individual
spline fits.

We can also overlay the centroid on the data, after rescaling the data to be between 0-1, like the centroids

```{r}
de_moanin_rescale = de_moanin_model
assay(de_moanin_rescale) = rescale_values(data=assay(de_moanin_model))
plot_splines_data(de_moanin_rescale,  
    centroid=kmeans_clusters$centroids[cluster_of_interest,], 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    subset_data=cluster2Genes[3:6],
    mar=c(1.5,2.5,2,0.1))
```
**EAP** I added the functionality to plot centroid over data, rather than just fit to data, but I'm not sure it makes much sense to include this. The `rescale_values` function is too sensitive to outliers. Would be better to rescale each centroid to scale of gene. If we had a helper function to do that, could easily add that to plot_splines_data (made issue on moanin), but probably right now should remove this.

### Assigning genes to clusters

Because there is variability in how well the genes fit a cluster, we would like to be able to score how well a gene fits a cluster. Furthermore, we arbitrarily chose a subset of genes based on our filter, and we would
like to have a mechanism to assign all genes to a cluster.

>>>>

These centroids are on a 0-1 scale, because of our rescaling of the spline
fits, and do not represent the actual gene expression level. In Figure \ref{fig:genesVsCentroids}, we plot a few
of the actual genes assigned to cluster 2 with the estimated centroid overlaid:

```{r genesVsCentroids, fig.height=6, fig.width=6, fig.cap="Genes from cluster 2"}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
plot_splines_data(de_moanin_model,  
    centroid=kmeans_clusters$centroids[cluster_of_interest,], 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    subset_data=cluster2Genes[3:6],
    mar=c(1.5,2.5,2,0.1))
```

### Assigning genes to clusters
As we can see, while these genes have some similarity with the pattern of the cluster centroids, these particularly genes are not the best examples of the cluster, in the sense of matching the centroid estimates. Because of this variability in how well the genes fit a cluster, we would like to be able to score how well a gene fits a cluster.

Furthermore, we arbitrarily chose a subset of genes based on our filter, and we would
like to have a mechanism to assign all genes to a cluster.
